MLH1 data report 

### 2017-11-15 1rmd_report.rmd
renamed to resolve

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
library(pwr)
library(plyr)
library(lattice)
library(dplyr)
setwd("C:/Users/alpeterson7/Documents/MLH1repo")
load(file="MLH1_data_setup.RData")
```

@@

```{r,echo=FALSE}

#set the order of another column, based on another variable (so that when)

@@

MLH1_data <- MLH1_data %>%
  arrange(category) %>%
  mutate(Original.Name = factor(Original.Name)) #another category that you want the order to match
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(category),])

@@

MLH1_data <- MLH1_data %>%
  arrange(strain, sex, mouse) %>%
  mutate(Original.Name = factor(Original.Name)) #another category that you want the order to match
# sort your dataframe, by the focal categories
MLH1_data$mouse <- factor(MLH1_data$mouse, levels=unique(MLH1_data$mouse))

ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci, fill= strain )) + geom_boxplot()  + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen", "green", "grey" ))
ff <- ff   + facet_wrap(~ sex, scales="free")

@@

```{r, histogram, echo=FALSE, fig.caption= "histograms", warning=FALSE, fig.align='center'}

histM <- ggplot(MLH1_data,(aes(adj_nMLH1.foci))) + xlim(c(16, 38))
histM <- histM + geom_histogram(stat = "bin", binwidth = 1)
histM <- histM + facet_wrap(~ category)
histM
```

@@

#MLH1_data$quality <- as.numeric(MLH1_data$quality) #this needs to be run for the subsetting to work
highest_qual_df <-  subset(MLH1_data, as.numeric(MLH1_data$quality) <= 2 )

@@

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7, 12, 14,16, 18) ]
#7, PERC. 12 CASTF, 14 HMI f , 16 SPRET f. 18 other

@@

```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE }
geom_hline(aes(yintercept = med, group = gr), colour = 'red')

for (gg in 1:length(plot_list) ){
  show(plot_list[gg])
  #invisible(lapply(obj, function(x) plot(x,main="some plot")))
}
```

>>>>

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
#setwd("C:/Users/alpeterson7/Documents/MLH1repo")
setwd("C:/Users/April/Desktop/MLH1repo")
load(file="MLH1_data_setup.RData")
```

@@

```{r,echo=FALSE}
#set the order of another column, based on another variable (so that when)

@@

@@

#reduncant
#MLH1_data <- MLH1_data %>%
 # arrange(strain, sex, mouse) %>%
#  mutate(Original.Name = factor(Original.Name)) #another category that you want the order to match
# sort your dataframe, by the focal categories
#MLH1_data$mouse <- factor(MLH1_data$mouse, levels=unique(MLH1_data$mouse))

ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci, fill= strain ))+geom_boxplot()+ ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen", "green", "grey" ))
ff <- ff   + facet_wrap(~ sex, scales="free")

@@

```{r, histogram, echo=FALSE, fig.caption= "histograms", warning=FALSE, fig.align='center'}
histM <- ggplot(MLH1_data,(aes(adj_nMLH1.foci))) + xlim(c(16, 38))
histM <- histM + geom_histogram(stat = "bin", binwidth = 1)
histM <- histM + facet_wrap(~ category)
histM
```

@@

#MLH1_data$quality <- as.numeric(MLH1_data$quality) #this needs to be run for the subsetting to work

highest_qual_df <-  subset(MLH1_data, as.numeric(MLH1_data$quality) <= 2 )

@@

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
#what is the purpose of this block

df_list <- split(MLH1_data, (MLH1_data$category))

#remove sections which are in category but have no data
df_list <- df_list[ -c(7, 12, 14,16, 18) ]
#7, PERC. 12 CASTF, 14 HMI f , 16 SPRET f. 18 other

@@

```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE }
geom_hline(aes(yintercept = med, group = gr), colour = 'red')
for (gg in 1:length(plot_list) ){
  show(plot_list[gg])
  #invisible(lapply(obj, function(x) plot(x,main="some plot")))
}
```
